### 2014-06-06 method.tex
minor changes

What is thus desired is a method which can compute an early feature which indicates the region priority, and then can use that same feature in the subsequent classification, with minimal computation that cannot be so amortized.  We formulate a cascade version of the RCNN architecture which has these desirable properties, and show that either alone or in concert with other methods below, it can effectively learn a "Timely" approach to the detection computation.

@@

We first tried to simply sort the regions by score and take batches in that sorted order.
Surprisingly, this naive method results in poor performance, and in fact can be worse than taking regions in an entirely random order.
We hypothesize that this is because the highest scoring regions may all be overlapping with each other, and only result in one detection after non-maximal suppression and other post-processing of detections.
Guided by this intuition, we consider a more cascade-like and dynamic approach to region selection.
We put regions in a random order, set a threshold such that only half of the unexamined regions score above it, take a batch of the above-threshold regions in their order, update the threshold, and repeat.

@@

We have fine-tuned an ``AlexNet'' \cite{Krizhevsky-NIPS-2012} CNN using the PASCAL VOC 2007 classification challenge.
Unlike the ILSVRC, the PASCAL VOC is a multi-label prediction task, with at times multiple correct labels for an image.
Accordingly, we implement cross-entropy loss layer to train a simple multi-label classifier with binary vector.

@@

Most ROIs that go through the CNN in R-CNN do not contain objects of interest, and are simply background.
It would be useful to quickly reject these regions, without expending the full amount of computation on them. Since most of the time is spend in the convolution layers, we introduce a reject layer after pool1, pool2, conv3 and conv4, this allows skipping the computation of the following convolutions. These reject layers were trained using the corresponding fine-tuned CNN.

@@

To estimate the saving on time by using the rejectors we timed the time spend to process 1000 regions (10 batches or 100) and the time expended in each of the first 3 layers:
\begin{itemize}
\item 1700 ms to process all the layers
\item 270 ms (15\%) in layer 1 (This includes conv1, relu1, pool1, norm1)
\item 360 ms (20\%) in layer 2 (This includes conv2, relu2, pool2, norm2)
\item 285 ms (15\%) in layer 3 (This includes conv3, relu3)
\end{itemize}

@@

At test time, I observe how many regions out of the batch size of 100 survive each round of thresholding, and then have a weighted average of a region lifetime in that batch. I multiply the standard batch time of 500ms by that average region lifetime to arrive at the batch time of the cascaded CNN.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\subsection{Region selection}\label{sec:dynamic}

>>>>

What is thus desired is a method which can compute an early feature which indicates the region priority, and then can use that same feature in the subsequent classification, with minimal computation that cannot be so amortized.  We formulate a cascade version of the RCNN architecture which has these desirable properties, and show that either alone or in concert with other methods below, it can effectively learn a ``Timely'' approach to the detection computation.

@@

We first tried to simply sort the regions by score and take batches in that sorted order.
Surprisingly, this naive method results in poor performance, and in fact can be worse than taking regions in an entirely random order.
We hypothesize that this is because the highest scoring regions may all be overlapping with each other, and only result in one detection after non-maximal suppression and other post-processing of detections.
Guided by this intuition, we consider a more dynamic approach to region selection:
we put regions in a random order, set a threshold such that only half of the unexamined regions score above it, take a batch of the above-threshold regions in their order, update the threshold, and repeat.

@@

We have fine-tuned an ``AlexNet'' \cite{Krizhevsky-NIPS-2012} CNN using the PASCAL VOC 2007 classification challenge.
Unlike the ILSVRC, the PASCAL VOC is a multi-label prediction task, with at times multiple correct labels for an image.
Accordingly, we implement a cross-entropy loss layer to train a simple multi-label classifier with binary vector.

@@

Most ROIs that go through the CNN in R-CNN do not contain objects of interest, and are simply background.
It would be useful to quickly reject these regions, without expending the full amount of computation on them. Since most of the time is spend in the convolution layers, we introduce a reject layer after layer 1, 2, and 3, this allows skipping the computation of the following convolutions. These reject layers were trained using the corresponding fine-tuned CNN.

@@

To estimate the saving on time by using the rejectors we timed the time spend to process 1000 regions (10 batches or 100) and the time expended in each of the first 3 layers:

\begin{itemize}
\item 1700 ms to process all the layers
\item 270 ms (15\%) in layer 1 (This includes \texttt{conv1}, \texttt{relu1}, \texttt{pool1}, \texttt{norm1})
\item 360 ms (20\%) in layer 2 (This includes \texttt{conv2}, \texttt{relu2}, \texttt{pool2}, \texttt{norm2})
\item 285 ms (15\%) in layer 3 (This includes \texttt{conv3}, \texttt{relu3})
\end{itemize}

@@

At test time, we observe how many regions out of the batch size of 100 survive each round of thresholding, and then have a weighted average of a region lifetime in that batch. We multiply the standard batch time of 500ms by that average region lifetime to arrive at the batch time of the cascaded CNN.

@@

### 2014-06-06 related_work.tex
minor changes

\paragraph{Object recognition with CNN}\label{object-recognition-with-cnn}
The recent success of deep convolutional neural networks (CNN) Alexnet \cite{Krizhevsky-NIPS-2012} on image classification tasks such as ImageNet \cite{deng2009cvpr} has spurred various investigations \cite{Girshick-CVPR-2014,Zou-CVPR-2014,Simonyan-ICLR-2014,Sermanet-ICLR-2014} how this success can be carried over to an detection task despite the prohibitive cost of evaluating such models densely in a naive manner. These previous attempts aim at reducing computational cost by reducing the search space of sliding window search by a bottom up window proposal scheme \cite{Girshick-CVPR-2014}, reducing computational overhead by sharing computation between windows to be evaluated \cite{Zou-CVPR-2014,Sermanet-ICLR-2014} as well as deriving a window sampling scheme that is based on the gradient of the network \cite{Simonyan-ICLR-2014}. All these method have in common that they rely on a fixed strategy and cannot adapt the computational scheme based on intermediate results, while we propose a dynamic scheme that steers computation based on intermediate outcomes in order to spend computation time most effectively. In contrast to previous work on shared dense computation layers in CNN classifiers for detection \cite{Sermanet-ICLR-2014}, we maintain effective canonicalization of regions and show its importance for achieving high performance.

@@

\paragraph{Dynamic selection}\label{dynamic-selection}
Most recently, learnt feature and classification deployment schemes based on budget aware policies have shown how to flexibly adapt computation at test time dependent on the input and intermediate results \cite{Karayev-NIPS-2012,karayev14cvpr}. We extend these ideas to the most recent developments of CNNs for visual object detection with a focus on deployment on highly parallel GPU computing hardware. In particular, we effectively combine  dense evaluation of shared, cheap feature with a fine-grained, dynamic execution policy reasoning on window proposals for more expensive features.

>>>>

\paragraph{Object recognition with CNN}\label{object-recognition-with-cnn}

The recent success of deep convolutional neural networks (CNN) such as Alexnet \cite{Krizhevsky-NIPS-2012} on image classification tasks such as ImageNet \cite{deng2009cvpr} has prompted many attempts to apply these computationally expensive methods to detection \cite{Girshick-CVPR-2014,Zou-CVPR-2014,Simonyan-ICLR-2014,Sermanet-ICLR-2014} .

These previous attempts aim at reducing computational cost by reducing the search space of sliding window search by a bottom up window proposal scheme \cite{Girshick-CVPR-2014}, reducing computational overhead by sharing computation between windows to be evaluated \cite{Zou-CVPR-2014,Sermanet-ICLR-2014}, or deriving a CNN-based window sampling scheme \cite{Simonyan-ICLR-2014}.
All these method have a fixed strategy and are unable to adapt their computational scheme based on intermediate results, while we propose a dynamic scheme that steers computation based on intermediate outcomes in order to spend computation time most effectively.

@@

\paragraph{Dynamic selection}\label{dynamic-selection}
Most recently, learnt feature and classification deployment schemes based on budget aware policies have shown how to flexibly adapt computation at test time dependent on the input and intermediate results \cite{Karayev-NIPS-2012,dulac2014}.
In particular, we combine  dense evaluation of shared, cheap feature with a fine-grained, dynamic execution policy reasoning on window proposals for more expensive features.
